# Cohort features

```{r}
# Libraries
suppressPackageStartupMessages(library(tidyverse))
library(ggcorrplot)

# Global
options(warn = -1)

# Scripts
source("summarize.R")

# Data
load("DF.Rdata")

glimpse(DF)
```

## Clinical and outcome features
Clinical and outcome features are analyzed at the patient level.

```{r}
# Tidying up the clinical data
CLINICAL <- DF %>% 
    group_by(registry_id) %>% 
    select(
        registry_id,
        age_dx,
        sex,
        fu_mo,
        recurrence_any,
        progression_stage_any,
        progression_grade_any,
        death
    ) %>% 
    distinct() %>%
    ungroup()

glimpse(CLINICAL)
```

### Age, in years
```{r}
CLINICAL %>% summarize_num(age_dx)
```

### Sex
```{r}
CLINICAL %>% summarize_fct(sex)
```

### Follow-up, in months
```{r}
CLINICAL %>% summarize_num(fu_mo)
```

### Tumor recurrence at any biopsy
```{r}
CLINICAL %>% summarize_fct(recurrence_any)
```

### Tumor grade progression at any biopsy
```{r}
CLINICAL %>% summarize_fct(progression_grade_any)
```

### Tumor stage progression at any biopsy
```{r}
CLINICAL %>% summarize_fct(progression_stage_any)
```

### Overall mortality
```{r}
CLINICAL %>% summarize_fct(death)
```

## Pathologic features
This section includes the pathologic features of the cases that were included in the dataset. For the histologic diagnosis, "CIS" includes carcinoma in situ and dysplasia, "LG" and "HG" mean low-grade and high-grade noninvasive papillary urothelial carcinoma, respectively.

```{r}
# Tidying up the pathologic data
PATHOLOGIC <- DF %>% 
    group_by(sp_id) %>% 
    select(
        sp_id,
        histo_dx,
        pt_stage,
        recurrence_next,
        progression_grade_next,
        progression_stage_next
    ) %>% 
    distinct() %>% 
    ungroup()

glimpse (PATHOLOGIC)
```

### Histologic diagnosis
```{r}
PATHOLOGIC %>% summarize_fct(histo_dx)
```

### pT stage
```{r}
PATHOLOGIC %>% summarize_fct(pt_stage)
```

### Tumor recurrence at next biopsy
```{r}
PATHOLOGIC %>% summarize_fct(recurrence_next)
```

### Tumor grade progression at next biopsy
```{r}
PATHOLOGIC %>% summarize_fct(progression_grade_next)
```

### Tumor stage progression at next biopsy
```{r}
PATHOLOGIC %>% summarize_fct(progression_stage_next)
```

## Biomarkers features
Biomarkers features were established at the TMA level.

### Biomarker distribution

```{r}
DF %>% 
    select(ck56:uroplakin) %>% 
    gather(key = "Biomarker", value = "Expression") %>% 
    summarize_nums(Expression, Biomarker)
```

### Biomarker and histology
#### CK5/6
```{r}
DF %>% 
    mutate(
        marker = ck56,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

#### CD44
```{r}
DF %>% 
    mutate(
        marker = cd44,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

#### CK20
```{r}
DF %>% 
    mutate(
        marker = ck20,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

#### GATA3
```{r}
DF %>% 
    mutate(
        marker = gata3,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

#### ER
```{r}
DF %>% 
    mutate(
        marker = er,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

#### HER2
```{r}
DF %>% 
    mutate(
        marker = her2,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

#### Uroplakin
```{r}
DF %>% 
    mutate(
        marker = uroplakin,
        feature = histo_dx
    ) %>% 
    summarize_nums(marker, feature)
```

### Biomarker and stage
#### CK5/6
```{r}
DF %>% 
    mutate(
        marker = ck56,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

#### CD44
```{r}
DF %>% 
    mutate(
        marker = cd44,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

#### CK20
```{r}
DF %>% 
    mutate(
        marker = ck20,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

#### GATA3
```{r}
DF %>% 
    mutate(
        marker = gata3,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

#### ER
```{r}
DF %>% 
    mutate(
        marker = er,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

#### HER2
```{r}
DF %>% 
    mutate(
        marker = her2,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

#### Uroplakin
```{r}
DF %>% 
    mutate(
        marker = uroplakin,
        feature = pt_stage
    ) %>% 
    summarize_nums(marker, feature)
```

### Correlation between biomarkers

```{r}
# A function to evaluate correlation between markers
COR <- function(data, x, y, label = NULL, ...) {
    # Data
    x = enquo(x)
    y = enquo(y)
    df <- data %>% 
        select(x = !! x, y = !! y)
    
    # Correlation test
    cor_tbl <- cor.test(df$x, df$y, ...) %>% 
        broom::tidy() %>% 
        mutate(
            label = label,
            coef = round(estimate, digits = 2),
            conf.low = round(conf.low, digits = 2),
            conf.high = round(conf.high, digits = 2),
            p.value = formatC(p.value, digits = 2, format = "fg")
        ) %>% 
        select(
            label, coef, conf.low, conf.high, p.value
        )
    
    # Returning the results
    return(cor_tbl)
}
```

```{r}
# Basal markers
ck56_cd44 <- DF %>% COR(ck56, cd44, "CK5/6 vs CD44")

# Luminal markers
ck20_her2 <- DF %>% COR(ck20, her2, "CK20 vs HER2/neu")
ck20_uroplakin <- DF %>% COR(ck20, uroplakin, "CK20 vs Uroplakin II")
her2_uroplakin <- DF %>% COR(her2, uroplakin, "HER2/neu vs Uroplakin II")

# Basal vs luminal markers
ck56_ck20 <- DF %>% COR(ck56, ck20, "CK5/6 vs CK20")
ck56_her2 <- DF %>% COR(ck56, her2, "CK5/6 vs HER2/neu")
ck56_uroplakin <- DF %>% COR(ck56, uroplakin, "CK5/6 vs Uroplakin II")
cd44_ck20 <- DF %>% COR(cd44, ck20, "CD44 vs CK20")
cd44_her2 <- DF %>% COR(cd44, her2, "CD44 vs HER2/neu")
cd44_uroplakin <- DF %>% COR(cd44, uroplakin, "CD44 vs Uroplakin II")

bind_rows(
    ck56_cd44,
    ck20_her2,
    ck20_uroplakin,
    her2_uroplakin,
    ck56_ck20,
    ck56_her2,
    ck56_uroplakin,
    cd44_ck20,
    cd44_her2,
    cd44_uroplakin
) %>% print()
```
