---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.1.1
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Regression models

```{r}
# Libraries
suppressPackageStartupMessages(library(tidyverse))
library(broom)
library(survival)
suppressPackageStartupMessages(library(survminer))

# Global
options(warn = -1)

# Scripts
source("summarize.R")

# Data
load("DF.Rdata")

glimpse(DF)
```

```{r}
# A function to define which statistics (v.g., median, max value) will be used for summarizing biomarkers expression
# If needed, changing this function will update the approach for the entire analysis
summarize_biomarker <- function(x) { mean(x, na.rm = TRUE) }

# Tidying up the data and summarizing expression
OUTCOME <- DF %>% 
    group_by(sp_id) %>% 
    summarize(
        ck56 = summarize_biomarker(ck56),
        cd44 = summarize_biomarker(cd44),
        ck20 = summarize_biomarker(ck20),
        er = summarize_biomarker(er),
        her2 = summarize_biomarker(her2),
        gata3 = summarize_biomarker(gata3),
        uroplakin = summarize_biomarker(uroplakin),
        pt_stage = unique(pt_stage),
        fu_mo = unique(fu_mo),
        recurrence_next = unique(recurrence_next),
        recurrence_any = unique(recurrence_any),
        progression_grade_next = unique(progression_grade_next),
        progression_grade_any = unique(progression_grade_any),
        progression_stage_next = unique(progression_stage_next),
        progression_stage_any = unique(progression_stage_any)
    ) %>% 
    mutate(
        pt = ifelse(
          pt_stage == "Tis" | pt_stage == "Ta",
          "Low pT stage (<pT1)", "High pT stage (pT1-pT2)"
        ),
        pt = fct_relevel(pt, "Low pT stage (<pT1)"),
        ck56_level = ifelse(
          ck56 > summarize_biomarker(ck56),
          "High CK5/6 expression", "Low CK5/6 expression"
        ),
        ck56_level = fct_relevel(ck56_level, "Low CK5/6 expression"),
        cd44_level = ifelse(
          cd44 > summarize_biomarker(cd44),
          "High CD44 expression", "Low CD44 expression"
        ),
        cd44_level = fct_relevel(cd44_level, "Low CD44 expression"),
        ck20_level = ifelse(
          ck20 > summarize_biomarker(ck20),
          "High CK20 expression", "Low CK20 expression"
        ),
        ck20_level = fct_relevel(ck20_level, "Low CK20 expression"),
        er_level = ifelse(
          er > summarize_biomarker(er),
          "High ER expression", "Low ER expression"
        ),
        er_level = fct_relevel(er_level, "Low CK20 expression"),
        her2_level = ifelse(
          her2 > summarize_biomarker(her2),
          "High HER2 expression", "Low HER2 expression"
        ),
        her2_level = fct_relevel(her2_level, "Low HER2 expression"),
        gata3_level = ifelse(
          gata3 > summarize_biomarker(gata3),
          "High GATA3 expression", "Low GATA3 expression"
        ),
        gata3_level = fct_relevel(gata3_level, "Low GATA3 expression"),
        uroplakin_level = ifelse(
          uroplakin > summarize_biomarker(uroplakin),
          "High Uroplakin expression", "Low Uroplakin expression"
        ),
        uroplakin_level = fct_relevel(uroplakin_level, "Low Uroplakin expression")
    )

glimpse(OUTCOME)
```

## CK5/6
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = ck56_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# Strings for outcomes
outcomes_str <- c(
    "Tumor recurrence at next biopsy diagnosis",
    "Tumor recurrence at any subsequent biopsy diagnosis",
    "Tumor grade progression at next biopsy diagnosis",
    "Tumor grade progression at any subsequent biopsy diagnosis",
    "Tumor stage progression at next biopsy diagnosis",
    "Tumor stage progression at any subsequent biopsy diagnosis"
)

# OR table for CK5/6
OR_ck56 <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("CK5/6"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_ck56
```

## CD44
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = cd44_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# OR table for CD44
OR_cd44 <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("CD44"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_cd44
```

## CK20
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = ck20_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# OR table for CK20
OR_ck20 <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("CK20"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_ck20
```

## ER
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = er_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# OR table for CK5/6
OR_er <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("ER"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_er
```

## HER2
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = her2_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# OR table for CK5/6
OR_her2 <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("HER2/neu"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_her2
```

## GATA3
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = gata3_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# OR table for CK5/6
OR_gata3 <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("GATA3"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_gata3
```

## Uroplakin
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = uroplakin_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
RN_marker <- OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
RA_marker <- OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
GN_marker <- OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
GA_marker <- OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
SN_marker <- OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
SA_marker <- OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

### Summary table
```{r}
# OR table for CK5/6
OR_uroplakin <- bind_rows(
    RN_marker,
    RA_marker,
    GN_marker,
    GA_marker,
    SN_marker,
    SA_marker
    ) %>% 
    mutate(
        outcome = outcomes_str,
        marker = c("Uroplakin II"),
        p.value = formatC(p.value, digits = 2, format = "fg", flag = "#"),
        conf.low = formatC(conf.low, digits = 3),
        conf.high = formatC(conf.high, digits = 3)
    ) %>% 
    select(
        marker, outcome, or, conf.low, conf.high, p.value
    ) 

OR_uroplakin
```

## Summary OR table
```{r}
summary_OR <- bind_rows(
    OR_ck56,
    OR_cd44,
    OR_ck20,
    OR_er,
    OR_her2,
    OR_gata3,
    OR_uroplakin
)
```

### Tumor recurrence at next biopsy
```{r}
summary_OR %>% 
  filter(outcome == "Tumor recurrence at next biopsy diagnosis") %>% 
  select(-outcome)
```

### Tumor recurrence at any biopsy
```{r}
summary_OR %>% 
  filter(outcome == "Tumor recurrence at any subsequent biopsy diagnosis") %>% 
  select(-outcome)
```

### Tumor grade progression at next biopsy
```{r}
summary_OR %>% 
  filter(outcome == "Tumor grade progression at next biopsy diagnosis") %>% 
  select(-outcome)
```

### Tumor grade progression at any biopsy
```{r}
summary_OR %>% 
  filter(outcome == "Tumor grade progression at any subsequent biopsy diagnosis") %>% 
  select(-outcome)
```

### Tumor stage progression at next biopsy
```{r}
summary_OR %>% 
  filter(outcome == "Tumor stage progression at next biopsy diagnosis") %>% 
  select(-outcome)
```

### Tumor stage progression at any biopsy
```{r}
summary_OR %>% 
  filter(outcome == "Tumor stage progression at any subsequent biopsy diagnosis") %>% 
  select(-outcome)
```

## Summary plot
Expression of ER and GATA3 were excluded from analysis, considering that most tumor cells lacked ER expression and most tumor cells were GATA3 positive. Marker expression was adjusted by pT stage.

```{r}
# A function to estimate odds ratios using binomial logistic regression
OR_tbl <- function(data, formula, marker, outcome, ...) {
  
  mdl <- glm(as.formula(formula), data = data, family = "binomial", ...)
  mdl_coef <- tidy(mdl) %>% 
    mutate(
      estimate = round(estimate, digits = 2),
      std.error = round(std.error, digits = 2),
      statistic = round(statistic, digits = 2),
      or = round(exp(estimate), digits = 2)
    )
  mdl_confint <- exp(confint_tidy(mdl)) %>% round(digits = 2)
  mdl_tbl <- bind_cols(mdl_coef, mdl_confint) %>% 
    select(or, conf.low, conf.high) %>% 
    mutate(
        marker = paste(marker),
        outcome = paste(outcome)
    )
  
  return(mdl_tbl[2 , ])

}
```

### Tumor recurrence at next biopsy
```{r}
outcome_str <- "Tumor recurrence at next biopsy diagnosis"
outcome_ck56 <- OUTCOME %>% OR_tbl(recurrence_next ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(recurrence_next ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(recurrence_next ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(recurrence_next ~ her2 + pt, "HER2/neu", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(recurrence_next ~ uroplakin + pt, "Uroplakin II", outcome_str)

recurrence_next_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(recurrence_next_marker)
```

### Tumor recurrence at any biopsy
```{r}
outcome_str <- "Tumor recurrence at any subsequent biopsy diagnosis"
outcome_ck56 <- OUTCOME %>% OR_tbl(recurrence_any ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(recurrence_any ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(recurrence_any ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(recurrence_any ~ her2 + pt, "HER2/neu", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(recurrence_any ~ uroplakin + pt, "Uroplakin II", outcome_str)

recurrence_any_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(recurrence_any_marker)
```

### Tumor stage progression at next biopsy
```{r}
outcome_str <- "Tumor stage progression at next biopsy diagnosis"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_stage_next ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_stage_next ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_stage_next ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_stage_next ~ her2 + pt, "HER2/neu", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_stage_next ~ uroplakin + pt, "Uroplakin II", outcome_str)

progression_stage_next_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_stage_next_marker)
```

### Tumor stage progression at any biopsy
```{r}
outcome_str <- "Tumor stage progression at any subsequent biopsy diagnosis"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_stage_any ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_stage_any ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_stage_any ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_stage_any ~ her2 + pt, "HER2/neu", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_stage_any ~ uroplakin + pt, "Uroplakin II", outcome_str)

progression_stage_any_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_stage_any_marker)
```

### Tumor grade progression at next biopsy
```{r}
outcome_str <- "Tumor grade progression at next biopsy diagnosis"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_grade_next ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_grade_next ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_grade_next ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_grade_next ~ her2 + pt, "HER2/neu", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_grade_next ~ uroplakin + pt, "Uroplakin II", outcome_str)

progression_grade_next_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_grade_next_marker)
```

### Tumor grade progression at any biopsy
```{r}
outcome_str <- "Tumor grade progression at any subsequent biopsy diagnosis"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_grade_any ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_grade_any ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_grade_any ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_grade_any ~ her2 + pt, "HER2/neu", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_grade_any ~ uroplakin + pt, "Uroplakin II", outcome_str)

progression_grade_any_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_grade_any_marker)
```

### Final table
```{r}
outcome_marker <- bind_rows(
  recurrence_next_marker,
  recurrence_any_marker,
  progression_grade_next_marker,
  progression_grade_any_marker,
  progression_stage_next_marker,
  progression_stage_any_marker
)

print(outcome_marker)
```

### Plot
Forest plots of biomarkers by outcome. Odds ratios (dots) with 95% confidence intervals (error bars) of expression levels and outcome. The dashed line corresponds to an odds ratio of 1. Odds ratios were adjusted by pT stage
```{r}
options(repr.plot.width = 10, repr.plot.height = 10)

outcome_marker <- outcome_marker %>% 
    mutate(
        outcome = fct_relevel(
            outcome,
            "Tumor recurrence at next biopsy diagnosis",
            "Tumor recurrence at any subsequent biopsy diagnosis",
            "Tumor grade progression at next biopsy diagnosis",
            "Tumor grade progression at any subsequent biopsy diagnosis",
            "Tumor stage progression at next biopsy diagnosis",
            "Tumor stage progression at any subsequent biopsy diagnosis"
        ),
        marker = fct_relevel(
            marker,
            "CK5/6",
            "CD44",
            "CK20",
            "HER2/neu",
            "Uroplakin II"            
        ),
        marker = fct_rev(marker)
    )

OR_Plot <- ggplot(outcome_marker, aes(x = marker, y = or, ymin = conf.low, ymax = conf.high)) +
    geom_pointrange() +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = 1, linetype = 2) +
    facet_wrap(~ outcome, ncol = 2) +
    coord_flip() +
    labs(x = NULL, y = NULL) +
    theme(
        strip.text.x = element_text(face = "bold", hjust = 0, size = 10)
    )

OR_Plot
```


```{r}
ggsave(
  filename = "Figs/BL-NMIBUC-OR.png",
  plot = OR_Plot,
  width = 10,
  height = 10,
  units = "in"
)
```
