---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.1.1
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Survival analysis

```{r}
# Libraries
suppressPackageStartupMessages(library(tidyverse))
library(broom)
library(survival)
suppressPackageStartupMessages(library(survminer))

# Global
options(warn = -1)

# Scripts
source("summarize.R")

# Data
load("DF.Rdata")

glimpse(DF)
```

```{r}
# A function to define which statistics (v.g., median, max value) will be used for summarizing biomarkers expression
# If needed, changing this function will update the approach for the entire analysis
summarize_biomarker <- function(x) { mean(x, na.rm = TRUE) }

# Tidying up the data and summarizing expression
OUTCOME <- DF %>% 
    group_by(sp_id) %>% 
    summarize(
        ck56 = summarize_biomarker(ck56),
        cd44 = summarize_biomarker(cd44),
        ck20 = summarize_biomarker(ck20),
        er = summarize_biomarker(er),
        her2 = summarize_biomarker(her2),
        gata3 = summarize_biomarker(gata3),
        uroplakin = summarize_biomarker(uroplakin),
        pt_stage = unique(pt_stage),
        fu_mo = unique(fu_mo),
        recurrence_next = unique(recurrence_next),
        recurrence_any = unique(recurrence_any),
        progression_grade_next = unique(progression_grade_next),
        progression_grade_any = unique(progression_grade_any),
        progression_stage_next = unique(progression_stage_next),
        progression_stage_any = unique(progression_stage_any)
    ) %>% 
    mutate(
        pt = ifelse(
          pt_stage == "Tis" | pt_stage == "Ta",
          "Low pT stage (<pT1)", "High pT stage (pT1-pT2)"
        ),
        pt = fct_relevel(pt, "Low pT stage (<pT1)"),
        ck56_level = ifelse(
          ck56 > summarize_biomarker(ck56),
          "High CK5/6 expression", "Low CK5/6 expression"
        ),
        ck56_level = fct_relevel(ck56_level, "Low CK5/6 expression"),
        cd44_level = ifelse(
          cd44 > summarize_biomarker(cd44),
          "High CD44 expression", "Low CD44 expression"
        ),
        cd44_level = fct_relevel(cd44_level, "Low CD44 expression"),
        ck20_level = ifelse(
          ck20 > summarize_biomarker(ck20),
          "High CK20 expression", "Low CK20 expression"
        ),
        ck20_level = fct_relevel(ck20_level, "Low CK20 expression"),
        er_level = ifelse(
          er > summarize_biomarker(er),
          "High ER expression", "Low ER expression"
        ),
        er_level = fct_relevel(er_level, "Low CK20 expression"),
        her2_level = ifelse(
          her2 > summarize_biomarker(her2),
          "High HER2 expression", "Low HER2 expression"
        ),
        her2_level = fct_relevel(her2_level, "Low HER2 expression"),
        gata3_level = ifelse(
          gata3 > summarize_biomarker(gata3),
          "High GATA3 expression", "Low GATA3 expression"
        ),
        gata3_level = fct_relevel(gata3_level, "Low GATA3 expression"),
        uroplakin_level = ifelse(
          uroplakin > summarize_biomarker(uroplakin),
          "High Uroplakin expression", "Low Uroplakin expression"
        ),
        uroplakin_level = fct_relevel(uroplakin_level, "Low Uroplakin expression")
    )

glimpse(OUTCOME)
```

## CK5/6
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = ck56_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```

## CD44
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = cd44_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```

## CK20
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = ck20_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```

## ER
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = er_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```

## HER2
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = her2_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```

## GATA3
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = gata3_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```

## Uroplakin
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = uroplakin_level)
```

### Tumor recurrence at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_next, biomarker_level)
```

### Tumor recurrence at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, recurrence_any, biomarker_level)
```

### Tumor grade progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_next, biomarker_level)
```

### Tumor grade progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_grade_any, biomarker_level)
```

### Tumor stage progression at next biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_next, biomarker_level)
```

### Tumor stage progression at any biopsy
```{r fig.width=9}
OUTCOME %>% summarize_surv(fu_mo, progression_stage_any, biomarker_level)
```
