---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.1.1
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Sequential expression of markers

```{r}
# Libraries
suppressPackageStartupMessages(library(tidyverse))

# Global
options(warn = -1, repr.plot.width = 10, repr.plot.height = 12)

# Sripts
source("summarize.R")

# Data
load("DF.Rdata")

glimpse(DF)
```

```{r}
# A function to define which statistics (v.g., median, max value) will be used for summarizing biomarkers expression
# If needed, changing this function will update the approach for the entire analysis
summarize_biomarker <- function(x) { mean(x, na.rm = TRUE) }

# Tidying up the data and summarizing expression
SEQ <- DF %>% 
  group_by(registry_id, sp_id) %>% 
      summarize(
        ck56 = summarize_biomarker(ck56),
        cd44 = summarize_biomarker(cd44),
        ck20 = summarize_biomarker(ck20),
        er = summarize_biomarker(er),
        her2 = summarize_biomarker(her2),
        gata3 = summarize_biomarker(gata3),
        uroplakin = summarize_biomarker(uroplakin),
        pt_stage = unique(pt_stage),
        fu_mo = unique(fu_mo),
        recurrence_next = unique(recurrence_next),
        recurrence_any = unique(recurrence_any),
        progression_grade_next = unique(progression_grade_next),
        progression_grade_any = unique(progression_grade_any),
        progression_stage_next = unique(progression_stage_next),
        progression_stage_any = unique(progression_stage_any),
        date_dx = unique(date_dx)
    ) %>% 
    arrange(date_dx) %>% 
    mutate(sequence = row_number()) %>% 
    ungroup() %>% 
    mutate(sequence = factor(sequence))

glimpse(SEQ)
```

```{r}
# A function to plot a panel of sequencial biomarker expression by outcome
plot_serial_panel <- function(data, biomarker) {
  
  biomarker = enquo(biomarker)
  df <- data %>% 
    mutate(biomarker = !! biomarker)
  
A <- df %>% 
  filter(!is.na(recurrence_next)) %>% 
  plot_serial(x = sequence, y = biomarker, group = registry_id, color = recurrence_next) +
  labs(title = "Tumor recurrence at next biopsy", tag = "A") +
  theme(legend.position = "none")

B <- df %>% 
  filter(!is.na(recurrence_any)) %>% 
  plot_serial(x = sequence, y = biomarker, group = registry_id, color = recurrence_any) +
  labs(title = "Tumor recurrence at any biopsy", tag = "B") +
  theme(legend.position = "none")

C <- df %>% 
  filter(!is.na(progression_grade_next)) %>% 
  plot_serial(x = sequence, y = biomarker, group = registry_id, color = progression_grade_next) +
  labs(title = "Tumor grade progression at next biopsy", tag = "C") +
  theme(legend.position = "none")

D <- df %>% 
  filter(!is.na(progression_grade_any)) %>% 
  plot_serial(x = sequence, y = biomarker, group = registry_id, color = progression_grade_any) +
  labs(title = "Tumor grade progression at any biopsy", tag = "D") +
  theme(legend.position = "none")

E <- df %>% 
  filter(!is.na(progression_stage_next)) %>% 
  plot_serial(x = sequence, y = biomarker, group = registry_id, color = progression_stage_next) +
  labs(title = "Tumor stage progression at next biopsy", tag = "C") +
  theme(legend.position = "none")

F <- df %>% 
  filter(!is.na(progression_stage_any)) %>% 
  plot_serial(x = sequence, y = biomarker, group = registry_id, color = progression_stage_any) +
  labs(title = "Tumor stage progression at any biopsy", tag = "D") +
  theme(legend.position = "none")

Fig_Serial <- gridExtra::grid.arrange(
  A, B, C, D, E, F,
  ncol = 2
)

return(Fig_Serial)

}
```

## CK5/6

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(ck56)
ggsave("Figs/BL-NMIBUC-SEQ-CK56.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## CD44

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(cd44)
ggsave("Figs/BL-NMIBUC-SEQ-CD44.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## CK20

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(ck20)
ggsave("Figs/BL-NMIBUC-SEQ-CK20.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## ER

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(er)
ggsave("Figs/BL-NMIBUC-SEQ-ER.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## HER2

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(her2)
ggsave("Figs/BL-NMIBUC-SEQ-HER2.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## GATA3

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(gata3)
ggsave("Figs/BL-NMIBUC-SEQ-GATA3.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## Uroplakin

```{r}
SEQ_BIOMARKER <- SEQ %>% plot_serial_panel(uroplakin)
ggsave("Figs/BL-NMIBUC-SEQ-UROPLAKIN.png", SEQ_BIOMARKER, width = 10, height = 12, units = "in")
```

## Combined plots
**Sequential expression of markers.** Each patient had between 2 and 5 sequential biopsies, shown in the x-axes. Mean percentages of positive cells are shown in the y-axes. Circles represent the expression value for each patient. Solid lines represent the trend between biopsies. No distinctive patterns were observed considering the expression across sequential biopsies. P values were calculated using the Kruskal-Wallis rank sum test.
```{r}
options(repr.plot.width = 10, repr.plot.height = 18)

SEQ_A <- SEQ %>% plot_ts(sequence, ck56, registry_id) +
  labs(title = "CK5/6",  tag = "A")

SEQ_B <- SEQ %>% plot_ts(sequence, cd44, registry_id) +
  labs(title = "CD44",  tag = "B")

SEQ_C <- SEQ %>% plot_ts(sequence, ck20, registry_id) +
  labs(title = "CK20",  tag = "C")

SEQ_D <- SEQ %>% plot_ts(sequence, er, registry_id) +
  labs(title = "ER",  tag = "D") +
  scale_y_continuous(limits = c(0, 100))

SEQ_E <- SEQ %>% plot_ts(sequence, her2, registry_id) +
  labs(title = "HER2",  tag = "E")

SEQ_F <- SEQ %>% plot_ts(sequence, gata3, registry_id) +
  labs(title = "GATA3",  tag = "F")

SEQ_G <- SEQ %>% plot_ts(sequence, uroplakin, registry_id) +
  labs(title = "Uroplakin",  tag = "G") +
  scale_y_continuous(limits = c(0, 100))

Plot_SEQ <- gridExtra::grid.arrange(
  SEQ_A, SEQ_B, SEQ_C, SEQ_D, SEQ_E, SEQ_F, SEQ_G,
  ncol = 1
)
```

```{r}
ggsave(
    filename = "Figs/BL-NMIBUC-SEQ.png",
    Plot_SEQ,
    width = 10,
    height = 18,
    units = "in"
)
```
