---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.1.1
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Regression models

```{r}
# Libraries
suppressPackageStartupMessages(library(tidyverse))
library(broom)
library(survival)
suppressPackageStartupMessages(library(survminer))

# Global
options(warn = -1)

# Scripts
source("summarize.R")

# Data
load("DF.Rdata")

glimpse(DF)
```

```{r}
# A function to define which statistics (v.g., median, max value) will be used for summarizing biomarkers expression
# If needed, changing this function will update the approach for the entire analysis
summarize_biomarker <- function(x) { mean(x, na.rm = TRUE) }

# Tidying up the data and summarizing expression
OUTCOME <- DF %>% 
    group_by(sp_id) %>% 
    summarize(
        ck56 = summarize_biomarker(ck56),
        cd44 = summarize_biomarker(cd44),
        ck20 = summarize_biomarker(ck20),
        er = summarize_biomarker(er),
        her2 = summarize_biomarker(her2),
        gata3 = summarize_biomarker(gata3),
        uroplakin = summarize_biomarker(uroplakin),
        pt_stage = unique(pt_stage),
        fu_mo = unique(fu_mo),
        recurrence_next = unique(recurrence_next),
        recurrence_any = unique(recurrence_any),
        progression_grade_next = unique(progression_grade_next),
        progression_grade_any = unique(progression_grade_any),
        progression_stage_next = unique(progression_stage_next),
        progression_stage_any = unique(progression_stage_any)
    ) %>% 
    mutate(
        pt = ifelse(
          pt_stage == "Tis" | pt_stage == "Ta",
          "Low pT stage (<pT1)", "High pT stage (pT1-pT2)"
        ),
        pt = fct_relevel(pt, "Low pT stage (<pT1)"),
        ck56_level = ifelse(
          ck56 > summarize_biomarker(ck56),
          "High CK5/6 expression", "Low CK5/6 expression"
        ),
        ck56_level = fct_relevel(ck56_level, "Low CK5/6 expression"),
        cd44_level = ifelse(
          cd44 > summarize_biomarker(cd44),
          "High CD44 expression", "Low CD44 expression"
        ),
        cd44_level = fct_relevel(cd44_level, "Low CD44 expression"),
        ck20_level = ifelse(
          ck20 > summarize_biomarker(ck20),
          "High CK20 expression", "Low CK20 expression"
        ),
        ck20_level = fct_relevel(ck20_level, "Low CK20 expression"),
        er_level = ifelse(
          er > summarize_biomarker(er),
          "High ER expression", "Low ER expression"
        ),
        er_level = fct_relevel(er_level, "Low CK20 expression"),
        her2_level = ifelse(
          her2 > summarize_biomarker(her2),
          "High HER2 expression", "Low HER2 expression"
        ),
        her2_level = fct_relevel(her2_level, "Low HER2 expression"),
        gata3_level = ifelse(
          gata3 > summarize_biomarker(gata3),
          "High GATA3 expression", "Low GATA3 expression"
        ),
        gata3_level = fct_relevel(gata3_level, "Low GATA3 expression"),
        uroplakin_level = ifelse(
          uroplakin > summarize_biomarker(uroplakin),
          "High Uroplakin expression", "Low Uroplakin expression"
        ),
        uroplakin_level = fct_relevel(uroplakin_level, "Low Uroplakin expression")
    )

glimpse(OUTCOME)
```

## CK5/6
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = ck56_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## CD44
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = cd44_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## CK20
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = ck20_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## ER
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = er_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## HER2
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = her2_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## GATA3
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = gata3_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## Uroplakin
```{r}
OUTCOME <- OUTCOME %>% 
  mutate(biomarker_level = uroplakin_level)
OUTCOME %>% summarize_fct(biomarker_level)
```

### Tumor recurrence at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_next ~ biomarker_level + pt)
```

### Tumor recurrence at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(recurrence_any ~ biomarker_level + pt)
```

### Tumor grade progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_next ~ biomarker_level + pt)
```

### Tumor grade progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_grade_any ~ biomarker_level + pt)
```

### Tumor stage progression at next biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_next ~ biomarker_level + pt)
```

### Tumor stage progression at any biopsy
#### Unadjusted
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level)
```

#### Adjusted by pT stage (low vs high)
```{r}
OUTCOME %>% OR(progression_stage_any ~ biomarker_level + pt)
```

## Summary plot
Expression of ER and GATA3 were excluded from analysis, considering that most tumor cells lacked ER expression and most tumor cells were GATA3 positive.
```{r}
# A function to estimate odds ratios using binomial logistic regression
OR_tbl <- function(data, formula, marker, outcome, ...) {
  
  mdl <- glm(as.formula(formula), data = data, family = "binomial", ...)
  mdl_coef <- tidy(mdl) %>% 
    mutate(
      estimate = round(estimate, digits = 2),
      std.error = round(std.error, digits = 2),
      statistic = round(statistic, digits = 2),
      or = round(exp(estimate), digits = 2)
    )
  mdl_confint <- exp(confint_tidy(mdl)) %>% round(digits = 2)
  mdl_tbl <- bind_cols(mdl_coef, mdl_confint) %>% 
    select(or, conf.low, conf.high) %>% 
    mutate(
        marker = paste(marker),
        outcome = paste(outcome)
    )
  
  return(mdl_tbl[2 , ])

}
```

### Tumor recurrence at next biopsy
```{r}
outcome_str <- "Tumor recurrence at next biopsy"
outcome_ck56 <- OUTCOME %>% OR_tbl(recurrence_next ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(recurrence_next ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(recurrence_next ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(recurrence_next ~ her2 + pt, "Her2", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(recurrence_next ~ uroplakin + pt, "Uroplakin", outcome_str)

recurrence_next_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(recurrence_next_marker)
```

### Tumor recurrence at any biopsy
```{r}
outcome_str <- "Recurrence at any biopsy"
outcome_ck56 <- OUTCOME %>% OR_tbl(recurrence_any ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(recurrence_any ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(recurrence_any ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(recurrence_any ~ her2 + pt, "Her2", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(recurrence_any ~ uroplakin + pt, "Uroplakin", outcome_str)

recurrence_any_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(recurrence_any_marker)
```

### Tumor stage progression at next biopsy
```{r}
outcome_str <- "Tumor stage progression at next biopsy"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_stage_next ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_stage_next ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_stage_next ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_stage_next ~ her2 + pt, "Her2", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_stage_next ~ uroplakin + pt, "Uroplakin", outcome_str)

progression_stage_next_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_stage_next_marker)
```

### Tumor stage progression at any biopsy
```{r}
outcome_str <- "Tumor stage progression at any biopsy"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_stage_any ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_stage_any ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_stage_any ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_stage_any ~ her2 + pt, "Her2", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_stage_any ~ uroplakin + pt, "Uroplakin", outcome_str)

progression_stage_any_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_stage_any_marker)
```

### Tumor grade progression at next biopsy
```{r}
outcome_str <- "Tumor grade progression at next biopsy"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_grade_next ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_grade_next ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_grade_next ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_grade_next ~ her2 + pt, "Her2", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_grade_next ~ uroplakin + pt, "Uroplakin", outcome_str)

progression_grade_next_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_grade_next_marker)
```

### Tumor grade progression at any biopsy
```{r}
outcome_str <- "Tumor grade progression at any biopsy"
outcome_ck56 <- OUTCOME %>% OR_tbl(progression_grade_any ~ ck56 + pt, "CK5/6", outcome_str)
outcome_ck20 <- OUTCOME %>% OR_tbl(progression_grade_any ~ ck20 + pt, "CK20", outcome_str)
outcome_cd44 <- OUTCOME %>% OR_tbl(progression_grade_any ~ cd44 + pt, "CD44", outcome_str)
outcome_her2 <- OUTCOME %>% OR_tbl(progression_grade_any ~ her2 + pt, "Her2", outcome_str)
outcome_uroplk <- OUTCOME %>% OR_tbl(progression_grade_any ~ uroplakin + pt, "Uroplakin", outcome_str)

progression_grade_any_marker <- bind_rows(
    outcome_uroplk, outcome_her2, outcome_ck20, outcome_cd44, outcome_ck56
)

print(progression_grade_any_marker)
```

### Final table
```{r}
outcome_marker <- bind_rows(
  recurrence_next_marker,
  recurrence_any_marker,
  progression_grade_next_marker,
  progression_grade_any_marker,
  progression_stage_next_marker,
  progression_stage_any_marker
)

print(outcome_marker)
```

### Plot
Forest plots of biomarkers by outcome. Odds ratios (dots) with 95% confidence intervals (error bars) of expression levels and outcome. The dashed line corresponds to an odds ratio of 1. Odds ratios were adjusted by pT stage
```{r}
options(repr.plot.width = 10, repr.plot.height = 10)

g <- ggplot(outcome_marker, aes(x = marker, y = or, ymin = conf.low, ymax = conf.high)) +
    geom_pointrange() +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = 1, linetype = 2) +
    facet_wrap(~ outcome, ncol = 2) +
    coord_flip() +
    labs(x = "", y = "")

OR_plot <- gridExtra::grid.arrange(
    g,
    ncol = 1
)
```


```{r}
ggsave(
  filename = "Figs/BL-NMIBUC-OR.png",
  plot = OR_plot,
  width = 10,
  height = 10,
  units = "in"
)
```
