---
title: "Basal and Luminal Markers in Non-Muscule Invasive Bladder Urothelial Carcinoma"
author: "Alcides Chaux, M.D."
subtitle: Preliminary Results
output:
  pdf_document: default
  html_document:
    theme: cerulean
---

***

```{r Data, echo = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE)
load("../Data/DF.Rdata")
library(moonBook)

```

## Methology
The following markers were evaluated

- CK5/6
- CK20
- CD44
- GATA3
- ER
- HER2
- Uroplakin

For each marker, the percentage of positive cells (extent) was recorded. Markers were also categorized as High/Low expression using the mean as the cutoffpoint

### Outcome endpoints
The analysis was carried out using paired events. For any case, the paired event consisted in the pair formed by 2 consecutive diagnoses during follow up. Thus, a case could have one or more paired events. For each marker, the considered outcomes included:

- __Tumor recurrence at next diagnosis:__ Tumor reappeared showing a similar or lower-grade/stage lession.
- __Tumor recurrence at any time:__ Tumor had recurred at least once during follow-up.
- __Tumor grade progression at next diagnosis:__ Tumor reappeared showing a higher-grade lession.
- __Tumor grade progression at any time:__ Tumor had showed grade progression at least once during follow-up.
- __Tumor stage progression at next diagnosis:__ Tumor reappeared showing a higher-stage lession.
- __Tumor stage progression at any time:__ Tumor had showed stage progression at least once during follow-up.

### Statistical analysis
For the asssociation and outcome analysis we used the Student's t-test and the Pearson's Chi-squared test. Data was analyzed and plots were generated using `r R.version.string`.

***

## Results

### Marker Extent and Level by Tumor Recurrence
#### __Table 1:__ Recurrence at next diagnosis
```{r}
# rec_next_time
mytable(
  rec_next_time ~ ck56 + ck20 + cd44 + gata3 + er + her2 + uroplakin +
    ck56_cat + ck20_cat + cd44_cat + gata3_cat + er_cat + her2_cat + uroplakin_cat,
  data = DF)

```

***

#### __Table 2:__ Recurrence at any time
```{r}
# rec_any_time
mytable(
  rec_any_time ~ ck56 + ck20 + cd44 + gata3 + er + her2 + uroplakin +
    ck56_cat + ck20_cat + cd44_cat + gata3_cat + er_cat + her2_cat + uroplakin_cat,
  data = DF)

```

***

### Marker Extent and Level by Grade Progression
#### __Table 3:__ Tumor grade progression at next diagnosis
```{r}
# grade_prog_next_time
mytable(
  grade_prog_next_time ~ ck56 + ck20 + cd44 + gata3 + er + her2 + uroplakin +
    ck56_cat + ck20_cat + cd44_cat + gata3_cat + er_cat + her2_cat + uroplakin_cat,
  data = DF)
```

***

#### __Table 4:__ Tumor grade progression at any time

```{r}
# grade_prog_any_time
mytable(
  grade_prog_any_time ~ ck56 + ck20 + cd44 + gata3 + er + her2 + uroplakin +
    ck56_cat + ck20_cat + cd44_cat + gata3_cat + er_cat + her2_cat + uroplakin_cat,
  data = DF)
```

***

### Marker Extend and Level by Stage Progression
#### __Table 5:__ Tumor stage progression at next diagnosis
```{r}
# pT_upstage_next_time
mytable(
  pT_upstage_next_time ~ ck56 + ck20 + cd44 + gata3 + er + her2 + uroplakin +
    ck56_cat + ck20_cat + cd44_cat + gata3_cat + er_cat + her2_cat + uroplakin_cat,
  data = DF)
```

***

#### __Table 5:__ Tumor stage progression at any time
```{r}
# pT_upstage_any_time
mytable(
  pT_upstage_any_time ~ ck56 + ck20 + cd44 + gata3 + er + her2 + uroplakin +
    ck56_cat + ck20_cat + cd44_cat + gata3_cat + er_cat + her2_cat + uroplakin_cat,
  data = DF)
```

***

__Last updated:__ `r date()`
